Prepping FAO aquaculture data

### 2022-01-28 analysis/validation_testing.Rmd
updated for resubmission!

@@

>>>>

cell_rast_df <- raster_df(food_raster) %>%
  dplyr::select(1:2)

## establish CRSs

## food 81km2 at equator 
eez_81 <- raster(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/data_type_A_eez/eez_validation_mask.tif"))
plot(raster::area(eez_81))
plot(eez_81)
cellStats(raster::area(eez_81), "mean")

test <- data.frame(raster::values(raster::area(eez_81)))

## 36km2 equal area
eez_36_cea <- raster(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/data_type_A_eez/eez_validation_mask_cea_36km.tif"))
plot(eez_36_cea)

new_crs <- "+proj=cea +lat_ts=45 +lon_0=0 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs"
new_raster <- raster(nrows=3000, ncols=4736, xmn=-14207430, xmx=14208570, ymn=-9000182, ymx=8999818, crs = new_crs)

## 25km2 equal area
eez_25_cea <- raster(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/data_type_A_eez/eez_validation_mask_cea_25km.tif"))

cea_25_crs <- crs(eez_25_cea)
plot(eez_25_cea)

## 1/4 degree cells 
eez_quart_cell <- raster(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/data_type_A_eez/eez_validation_mask_quarter_degree.tif"))

quarter_crs <- crs(eez_quart_cell)

@@

Read in validation dataset

```{r}
validation_all <- readRDS(file.path("data/all_validation_farms_resubmission.rds"))  %>%
  mutate(species_group = case_when(type == "salmon" ~ "Salmonidae fish",
                          type == "bivalve" ~ "Unfed or algae fed bivalve molluscs",
                          type == "shrimp" ~ "Shrimps and prawns", 
                          type == "tuna" ~ "Bluefin tuna", 
                          type == "marine_fish_general" ~ "General marine fish"))

table_3 <- read_csv("analysis/tables/SI_table_3.csv")

iso <-   data.frame(iso3c = countrycode(table_3$country, origin = 'country.name', destination = 'iso3c'))

table_3_iso3c <- table_3 %>%
  cbind(iso)

data_type_val <- validation_all %>%
  left_join(table_3_iso3c, by = c("iso3c", "species_group"))

data_type_A <- data_type_val %>%
 filter(data_type_2 %in% c("A"))

table_3_A <- table_3_iso3c %>%
  filter(data_type_2 %in% c("A"))

Split data

```{r}
validation_farms <- data_type_A %>%
 filter(source == "modeled validation") %>%
  mutate(count_farms = 1)

val_farms_cea_36 <- validation_farms %>%
  st_transform(crs = new_crs)

val_farms_cea_25 <- validation_farms %>%
  st_transform(crs = cea_25_crs)

val_farms_quarter <- validation_farms %>%
  st_transform(crs = quarter_crs)

real_farms <- data_type_A %>%
  filter(source == "real") %>%
  mutate(count_farms = 1)

real_farms_cea_36 <- real_farms %>%
  st_transform(crs = new_crs)

real_farms_cea_25 <- real_farms %>%
  st_transform(crs = cea_25_crs)

real_farms_quart <- real_farms %>%
  st_transform(crs = quarter_crs)
```

Rasterize data to count number of farms per raster cell with 36km2 equal area

val_rast <- rasterize(val_farms_cea_36, new_raster, field = "count_farms", fun = "sum")
plot(val_rast)

cellStats(val_rast, "sum") # 8552

plot(val_rast, col = "black")
#s <- raster::select(val_rast)
#plot(s)

real_rast <- rasterize(real_farms_cea_36, new_raster, field = "count_farms", fun = "sum")
plot(real_rast)

cellStats(real_rast, "sum") # 8552
plot(real_rast, col = "black")

rast_stack <- stack(val_rast, real_rast)
cellStats(rast_stack, "sum")

# layer.1 layer.2 
#    8552    8552

Use our EEZ mask to create a confusion matrix for CEA 36km2 cell sizes

 - AUC of ~0.60
```{r}

plot(eez_36_cea, col = "black")

world_coast <- as.data.frame(eez_36_cea) %>%
  mutate(cell = row_number()) %>%
  filter(!is.na(eez_validation_mask_cea_36km))

eez_cells_df <- as.data.frame(rast_stack) %>%
  rename("predicted" = "layer.1", "real" = "layer.2") %>%
  mutate(pred_count = ifelse(predicted >=1, 1, 0),
         real_mod_count = ifelse(predicted >=1&real>=1, 1, 0)) %>%
  mutate(real_count = ifelse(real>=1,1,0)) %>%
  mutate(pred_count = ifelse(is.na(pred_count), 0, pred_count),
         real_count = ifelse(is.na(real_count), 0, real_count), 
         real = ifelse(is.na(real), 0, real),
         predicted = ifelse(is.na(predicted), 0, predicted)) %>%
  mutate(cell = row_number()) %>% 
  filter(cell %in% c(world_coast$cell))

sum(eez_cells_df$predicted, na.rm = TRUE) # 8535

sum(eez_cells_df$real, na.rm = TRUE) # 8473

## still missing some farms.. but nothing egregious. This is probably ok. The results wouldn't change much even if we had the extra ~80 farms

test <- rast_stack*eez_36_cea

cellStats(test,"sum") 
# layer.1 layer.2 
#    8535    8473

## we are losing some farms...

#### make a confusion matrix

confusion_mat <- caret::confusionMatrix(data = as.factor(eez_cells_df$pred_count), reference = as.factor(eez_cells_df$real_count))

confusion_mat

# Confusion Matrix and Statistics
#           Reference
# Prediction       0       1
#          0 1171909    2552
#          1    2721     682
#                                           
#                Accuracy : 0.9955          
#                  95% CI : (0.9954, 0.9956)
#     No Information Rate : 0.9973          
#     P-Value [Acc > NIR] : 1.00000         
#                                           
#                   Kappa : 0.2033          
#                                           
#  Mcnemar's Test P-Value : 0.02069         
#                                           
#             Sensitivity : 0.9977          
#             Specificity : 0.2109          
#          Pos Pred Value : 0.9978          
#          Neg Pred Value : 0.2004          
#              Prevalence : 0.9973          
#          Detection Rate : 0.9949          
#    Detection Prevalence : 0.9971          
#       Balanced Accuracy : 0.6043          
#                                           
#        'Positive' Class : 0

# library(pROC)
# roc(eez_cells_df$real_count, eez_cells_df$pred_count, plot = TRUE) # 0.6019
# 
# 
# library(pROC)
# library(randomForest)
# 
# 
# roc(eez_cells_df$real_count, eez_cells_df$pred_count, plot = TRUE, percent = TRUE, xlab = "False Positive Percentage", ylab = "True Positive Percentage", col = "#377eb8", lwd = 4, print.auc = TRUE) # 0.6068
# 
# roc.info <- roc(eez_cells_df$real_count, eez_cells_df$pred_count, legacy.axes = TRUE)
# 
# roc.df <- data.frame(tpp = roc.info$sensitivities*100,
#                      fpp = (1-roc.info$specificities)*100,
#                      thresholds = roc.info$thresholds)
# 
# 
# #### ROC curve try #2
# # https://www.datatechnotes.com/2019/03/how-to-create-roc-curve-in-r.html
# 
# library(ROCR)
#   
#  
# pred = eez_cells_df$pred_count
# 
# pred = prediction(pred, eez_cells_df$real_count)
# 
# perf = performance(pred, "acc")
# plot(perf)
# 
# perf_cost <- performance(pred, "cost")
# plot(perf_cost)
# 
# roc = performance(pred, "tpr", "fpr")
# 
# plot(roc, colorize = T, lwd=2)
# abline(a=0, b=1)
# 
# auc = performance(pred, measure = "auc")
# print(auc@y.values)
# # 0.6091016

Use our EEZ mask to create a confusion matrix for CEA 25km2 cell sizes

 - AUC of ~0.59 - worse than 36km2... makes sense! 
```{r}

val_rast <- rasterize(val_farms_cea_25, eez_25_cea, field = "count_farms", fun = "sum")
plot(val_rast)

cellStats(val_rast, "sum")

plot(val_rast, col = "black")
#s <- raster::select(val_rast)
#plot(s)

real_rast <- rasterize(real_farms_cea_25, eez_25_cea, field = "count_farms", fun = "sum")
plot(real_rast)

cellStats(real_rast, "sum") # 8552
plot(real_rast, col = "black")

rast_stack <- stack(val_rast, real_rast)
cellStats(rast_stack, "sum")

# layer.1 layer.2 
#    8552    8552

plot(eez_25_cea, col = "black")

world_coast <- as.data.frame(eez_25_cea) %>%
  mutate(cell = row_number()) %>%
  filter(!is.na(eez_validation_mask_cea_25km))

eez_cells_df <- as.data.frame(rast_stack) %>%
  rename("predicted" = "layer.1", "real" = "layer.2") %>%
  mutate(pred_count = ifelse(predicted >=1, 1, 0),
         real_mod_count = ifelse(predicted >=1&real>=1, 1, 0)) %>%
  mutate(real_count = ifelse(real>=1,1,0)) %>%
  mutate(pred_count = ifelse(is.na(pred_count), 0, pred_count),
         real_count = ifelse(is.na(real_count), 0, real_count), 
         real = ifelse(is.na(real), 0, real),
         predicted = ifelse(is.na(predicted), 0, predicted)) %>%
  mutate(cell = row_number()) %>% 
  filter(cell %in% c(world_coast$cell))

sum(eez_cells_df$predicted, na.rm = TRUE) # 8536

sum(eez_cells_df$real, na.rm = TRUE) # 8482

## still missing some farms.. but nothing egregious. This is probably ok. The results wouldn't change much even if we had the extra ~80 farms. This is likely due to reprojection weirdness

test <- rast_stack*eez_25_cea

cellStats(test,"sum") 
# layer.1 layer.2 
#    8536    8482

#### make a confusion matrix

confusion_mat <- caret::confusionMatrix(data = as.factor(eez_cells_df$pred_count), reference = as.factor(eez_cells_df$real_count))

confusion_mat

# Confusion Matrix and Statistics
# 
#           Reference
# Prediction       0       1
#          0 1689310    2929
#          1    3100     639
#                                           
#                Accuracy : 0.9964          
#                  95% CI : (0.9964, 0.9965)
#     No Information Rate : 0.9979          
#     P-Value [Acc > NIR] : 1.00000         
#                                           
#                   Kappa : 0.1731          
#                                           
#  Mcnemar's Test P-Value : 0.02857         
#                                           
#             Sensitivity : 0.9982          
#             Specificity : 0.1791          
#          Pos Pred Value : 0.9983          
#          Neg Pred Value : 0.1709          
#              Prevalence : 0.9979          
#          Detection Rate : 0.9961          
#    Detection Prevalence : 0.9978          
#       Balanced Accuracy : 0.5886          
#                                           
#        'Positive' Class : 0

Use our EEZ mask to create a confusion matrix for 0.25 X 0.25 degree cell sizes (about 769.3152km2 at equator). Average cell size is 490.3108 km2

 - AUC of ~72.05 ; makes sense that is it better!

```{r}
test <- raster::area(eez_quart_cell)

cellStats(test, "mean") # 490.3108

mean(test@data@values) # 490.3108

val_rast <- rasterize(val_farms_quarter, eez_quart_cell, field = "count_farms", fun = "sum")
plot(val_rast)

cellStats(val_rast, "sum")

plot(val_rast, col = "black")

real_rast <- rasterize(real_farms_quart, eez_quart_cell, field = "count_farms", fun = "sum")
plot(real_rast)

cellStats(real_rast, "sum") # 8552
plot(real_rast, col = "black")

rast_stack <- stack(val_rast, real_rast)
cellStats(rast_stack, "sum")

# layer.1 layer.2 
#    8552    8552

plot(eez_quart_cell, col = "black")

world_coast <- as.data.frame(eez_quart_cell) %>%
  mutate(cell = row_number()) %>%
  filter(!is.na(eez_validation_mask_quarter_degree))

eez_cells_df <- as.data.frame(rast_stack) %>%
  rename("predicted" = "layer.1", "real" = "layer.2") %>%
  mutate(pred_count = ifelse(predicted >=1, 1, 0),
         real_mod_count = ifelse(predicted >=1&real>=1, 1, 0)) %>%
  mutate(real_count = ifelse(real>=1,1,0)) %>%
  mutate(pred_count = ifelse(is.na(pred_count), 0, pred_count),
         real_count = ifelse(is.na(real_count), 0, real_count), 
         real = ifelse(is.na(real), 0, real),
         predicted = ifelse(is.na(predicted), 0, predicted)) %>%
  mutate(cell = row_number()) %>% 
  filter(cell %in% c(world_coast$cell))

sum(eez_cells_df$predicted, na.rm = TRUE) # 8124

sum(eez_cells_df$real, na.rm = TRUE) # 8173

## still missing some farms..

test <- rast_stack*eez_quart_cell

cellStats(test,"sum") 
# layer.1 layer.2 
#    8124    8173

#### make a confusion matrix

confusion_mat <- caret::confusionMatrix(data = as.factor(eez_cells_df$pred_count), reference = as.factor(eez_cells_df$real_count))

confusion_mat

# Confusion Matrix and Statistics
# 
#           Reference
# Prediction     0     1
#          0 84570   639
#          1   902   514
#                                           
#                Accuracy : 0.9822          
#                  95% CI : (0.9813, 0.9831)
#     No Information Rate : 0.9867          
#     P-Value [Acc > NIR] : 1               
#                                           
#                   Kappa : 0.3912          
#                                           
#  Mcnemar's Test P-Value : 2.486e-11       
#                                           
#             Sensitivity : 0.9894          
#             Specificity : 0.4458          
#          Pos Pred Value : 0.9925          
#          Neg Pred Value : 0.3630          
#              Prevalence : 0.9867          
#          Detection Rate : 0.9763          
#    Detection Prevalence : 0.9837          
#       Balanced Accuracy : 0.7176          
#                                           
#        'Positive' Class : 0

Use our suitability mask to create a confusion matrix for XX degree cell sizes (about 81km2 at equator, ~10km of coastline) with data type A real farms

 - What % of data type A real farms fall into a suitable cell?
 - What % fall out of a suitable cell? 
 - What % of suitable cells do not have any farms in them? 
 - etc.

At 5 arc minute resolution (~10 km of coastline at the equator), when comparing our suitable areas to data type A real farms, we have a balanced accuracy of 0.81. Conducting this same analysis at a coarser resolution of 0.25 degrees (~30 km of coastline at the equator), we see a higher balanced accuracy of xx. Given this, we suggest utilizing our maps at a resolution of 5 arc minutes or larger, as 5 arc minutes produces a defensible accuracy, and aligns with other types of food production maps (e.g. MAPSPAM, FAO, etc).

When comparing to the coarser resolution of 0.25 degrees, the AUC jumps to 0.84.

suitability_81 <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/suitability_rasts/ocean_land_suitability.tif")
plot(suitability_81)

real_rast <- rasterize(real_farms 
                       , 
                       suitability_81, field = "count_farms", fun = "sum")

plot(real_rast, col = 'red')

cellStats(real_rast, "sum") # 8179
plot(real_rast, col = "black")

# norway_suit <- raster::crop(suitability_81, extent(-25, 50, 50, 75))
# norway_farm <- raster::crop(real_rast, extent(-25, 50, 50, 75))
# 
# plot(norway_suit)
# plot(norway_farm, add = TRUE, col = "red")
# 
# chile_suit <- raster::crop(suitability_81, extent(-80, -70, -44, -40))
# chile_farm <- raster::crop(real_rast, extent(-80, -70, -44, -40))
# 
# plot(chile_suit)
# plot(chile_farm, add = TRUE, col = "red")
# 
real_suit_stack <- stack(real_rast, suitability_81)

real_suit_df <- as.data.frame(real_suit_stack) %>%
  mutate(layer_count = ifelse(layer >=1, 1, 0),
         suit_count = ifelse(ocean_land_suitability >=1, 1, 0)) %>%
  mutate(layer_count = ifelse(is.na(layer_count), 0, layer_count),
         suit_count = ifelse(is.na(suit_count), 0, suit_count))
# 
# 
# analysis1 <- real_suit_df %>%
#   filter(layer >= 1, ocean_land_suitability == 1)
# 
# sum(analysis1$layer) # 8179
# 5277/8179 # 0.6451889 = 65% of real farms fall into suitable areas...
# 
# analysis2 <- real_suit_df %>%
#   filter(layer >= 1, is.na(ocean_land_suitability))
# 
# sum(analysis2$layer) # 2902
# 
# 2902/8179 # 35% fall out of suitable areas

confusion_mat <- caret::confusionMatrix(data = as.factor(real_suit_df$suit_count), reference = as.factor(real_suit_df$layer_count))

confusion_mat

# Confusion Matrix and Statistics
# 
#           Reference
# Prediction       0       1
#          0 6402310     932
#          1  118298    1660
#                                           
#                Accuracy : 0.9817          
#                  95% CI : (0.9816, 0.9818)
#     No Information Rate : 0.9996          
#     P-Value [Acc > NIR] : 1               
#                                           
#                   Kappa : 0.0263          
#                                           
#  Mcnemar's Test P-Value : <2e-16          
#                                           
#             Sensitivity : 0.98186         
#             Specificity : 0.64043         
#          Pos Pred Value : 0.99985         
#          Neg Pred Value : 0.01384         
#              Prevalence : 0.99960         
#          Detection Rate : 0.98147         
#    Detection Prevalence : 0.98161         
#       Balanced Accuracy : 0.81114         
#                                           
#        'Positive' Class : 0

#### Now look at other resolutions

## 36km2 equal area
suitability_36 <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/suitability_rasts/ocean_land_suit_36km.tif")
plot(suitability_36)

real_rast <- rasterize(real_farms_cea_36
                       , 
                       suitability_36, field = "count_farms", fun = "sum")

plot(real_rast, col = 'red')

cellStats(real_rast, "sum") # 8552
plot(real_rast, col = "black")

real_suit_stack <- stack(real_rast, suitability_36)

real_suit_df <- as.data.frame(real_suit_stack) %>%
  mutate(layer_count = ifelse(layer >=1, 1, 0),
         suit_count = ifelse(ocean_land_suit_36km >=1, 1, 0)) %>%
  mutate(layer_count = ifelse(is.na(layer_count), 0, layer_count),
         suit_count = ifelse(is.na(suit_count), 0, suit_count))

analysis1 <- real_suit_df %>%
  filter(layer >= 1, ocean_land_suit_36km == 1)

sum(analysis1$layer) # 5505
5505/8552 # 0.6437091 = 64% of real farms fall into suitable areas...

confusion_mat <- caret::confusionMatrix(data = as.factor(real_suit_df$suit_count), reference = as.factor(real_suit_df$layer_count))

confusion_mat

# Confusion Matrix and Statistics
# 
#           Reference
# Prediction        0        1
#          0 13967424     1337
#          1   237288     1951
#                                           
#                Accuracy : 0.9832          
#                  95% CI : (0.9831, 0.9833)
#     No Information Rate : 0.9998          
#     P-Value [Acc > NIR] : 1               
#                                           
#                   Kappa : 0.0156          
#                                           
#  Mcnemar's Test P-Value : <2e-16          
#                                           
#             Sensitivity : 0.983295        
#             Specificity : 0.593370        
#          Pos Pred Value : 0.999904        
#          Neg Pred Value : 0.008155        
#              Prevalence : 0.999769        
#          Detection Rate : 0.983068        
#    Detection Prevalence : 0.983162        
#       Balanced Accuracy : 0.788332        
#                                           
#        'Positive' Class : 0

# This makes sense given the finer resolution

## 25km2 equal area
suitability_25 <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/suitability_rasts/ocean_land_suit_25km.tif")
plot(suitability_25)

real_rast <- rasterize(real_farms_cea_25
                       , 
                       suitability_25, field = "count_farms", fun = "sum")

plot(real_rast, col = 'red')

cellStats(real_rast, "sum") # 8552
plot(real_rast, col = "black")

real_suit_stack <- stack(real_rast, suitability_25)

real_suit_df <- as.data.frame(real_suit_stack) %>%
  mutate(layer_count = ifelse(layer >=1, 1, 0),
         suit_count = ifelse(ocean_land_suit_25km >=1, 1, 0)) %>%
  mutate(layer_count = ifelse(is.na(layer_count), 0, layer_count),
         suit_count = ifelse(is.na(suit_count), 0, suit_count))

analysis1 <- real_suit_df %>%
  filter(layer >= 1, ocean_land_suit_25km == 1)

sum(analysis1$layer) # 5518
5518/8552 # 0.6452292 = 65% of real farms fall into suitable areas...

confusion_mat <- caret::confusionMatrix(data = as.factor(real_suit_df$suit_count), reference = as.factor(real_suit_df$layer_count))

confusion_mat

# Confusion Matrix and Statistics
# 
#           Reference
# Prediction        0        1
#          0 20112053     1505
#          1   343120     2122
#                                           
#                Accuracy : 0.9832          
#                  95% CI : (0.9831, 0.9832)
#     No Information Rate : 0.9998          
#     P-Value [Acc > NIR] : 1               
#                                           
#                   Kappa : 0.0118          
#                                           
#  Mcnemar's Test P-Value : <2e-16          
#                                           
#             Sensitivity : 0.983226        
#             Specificity : 0.585057        
#          Pos Pred Value : 0.999925        
#          Neg Pred Value : 0.006146        
#              Prevalence : 0.999823        
#          Detection Rate : 0.983051        
#    Detection Prevalence : 0.983125        
#       Balanced Accuracy : 0.784141        
#                                           
#        'Positive' Class : 0

## quarter degree cells

suitability_quart <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/suitability_rasts/ocean_land_suit_quart.tif")
plot(suitability_quart)

real_rast <- rasterize(real_farms_quart
                       , 
                       suitability_quart, field = "count_farms", fun = "sum")

plot(real_rast, col = 'red')

cellStats(real_rast, "sum") # 8179
plot(real_rast, col = "black")

real_suit_stack <- stack(real_rast, suitability_quart)

real_suit_df <- as.data.frame(real_suit_stack) %>%
  mutate(layer_count = ifelse(layer >=1, 1, 0),
         suit_count = ifelse(ocean_land_suit_quart >=1, 1, 0)) %>%
  mutate(layer_count = ifelse(is.na(layer_count), 0, layer_count),
         suit_count = ifelse(is.na(suit_count), 0, suit_count))

analysis1 <- real_suit_df %>%
  filter(layer >= 1, ocean_land_suit_quart == 1)

sum(analysis1$layer) # 5380
5380/8179 # 0.6577821 = 66% of real farms fall into suitable areas...

confusion_mat <- caret::confusionMatrix(data = as.factor(real_suit_df$suit_count), reference = as.factor(real_suit_df$layer_count))

confusion_mat

# Confusion Matrix and Statistics
# 
#           Reference
# Prediction      0      1
#          0 709283    325
#          1  13933    779
#                                         
#                Accuracy : 0.9803        
#                  95% CI : (0.98, 0.9806)
#     No Information Rate : 0.9985        
#     P-Value [Acc > NIR] : 1             
#                                         
#                   Kappa : 0.0959        
#                                         
#  Mcnemar's Test P-Value : <2e-16        
#                                         
#             Sensitivity : 0.98073       
#             Specificity : 0.70562       
#          Pos Pred Value : 0.99954       
#          Neg Pred Value : 0.05295       
#              Prevalence : 0.99848       
#          Detection Rate : 0.97924       
#    Detection Prevalence : 0.97969       
#       Balanced Accuracy : 0.84318       
#                                         
#        'Positive' Class : 0  
```

```{r}
# gentry <- raster(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/suitability_rasts/gentry/karakoenig"))
```

### 2022-01-28 marine/STEP1_species_groups/STEP1_species_groups.Rmd
updated for resubmission!

test <- fao_1 %>%
  dplyr::filter(aq_group == "salmonids")
sum(test$total_tonnes) #

@@

38731.97/29662247 # we exclude around 0.1% of marine aquaculture
```

>>>>

test <- fao_1 %>%
  dplyr::filter(aq_group == "salmonids")
sum(test$tonnes) # 2753752

@@

38731.97/29662247 # we exclude around 0.1% of marine aquaculture

## what is the proportion of marine salmon aquaculture that we include?

# we include 2753752 tonnes of marien salmon aquaculture
fao_1 <- read.csv(here("data/fao_aquaculture_clean.csv")) %>%
 filter(environment %in% c("Marine", "Brackishwater")) %>%
  left_join(aq_groups) %>%
  dplyr::filter(year == 2017,
                !is.na(value),
                !is.na(aq_group)) %>%
  # dplyr::filter(value < 500) %>%
  dplyr::filter(aq_group == "salmonids") %>%
  group_by(aq_group, country, species, year) %>%
  summarise(tonnes = sum(value)) %>%
  ungroup()  %>%
  # dplyr::filter(tonnes >= 500) %>%
  group_by(country, year) %>%
  summarise(total_tonnes = sum(tonnes))# %>%
 # arrange(aq_group)

sum(fao_1$total_tonnes) # 2754748

2753752/2754748 # we include 0.9996384

## What proportion does freshwater salmon production account for? 
fao_1 <- read.csv(here("data/fao_aquaculture_clean.csv")) %>%
 # filter(environment %in% c("Marine", "Brackishwater")) %>%
  left_join(aq_groups) %>%
  dplyr::filter(year == 2017, 
                Taxon_code %in% c(NA, "F"),
                aq_group %in% c(NA, "salmonids")) %>%
  dplyr::filter(aq_group == "salmonids"|str_detect(species, "trout|Trout|salmon|Salmon|char|Char|whitefish")) %>%
  # dplyr::filter(year == 2017,
               # !is.na(value)) %>%
                #!is.na(aq_group)) %>%
  # dplyr::filter(value < 500) %>%
  # dplyr::filter(aq_group == "salmonids") %>%
  group_by(aq_group, country, species, year, environment) %>%
  summarise(tonnes = sum(value)) %>%
  ungroup()  %>%
  # dplyr::filter(tonnes >= 500) %>%
  group_by(environment) %>%
  summarise(total_tonnes = sum(tonnes, na.rm = TRUE))# %>%
 # arrange(aq_group)

fao_1

# A tibble: 3 × 2
#   environment   total_tonnes
#   <chr>                <dbl>
# 1 Brackishwater       28086.
# 2 Freshwater         676537.
# 3 Marine            2726662.

2726662 + 28086 # 2754748

676537/2754748 # 0.2455894
```
